---
title: "Using rdomains"
author: "Gaurav Sood"
date: "`r Sys.Date()`"
vignette: >
  %\VignetteIndexEntry{Illustrating use of rdomains}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### rdomains: Get the category of content hosted by a domain


#### Install and Load the package

The latest development version of the package will always be on GitHub. To install the package from GitHub and to load the installed package:

```{r, eval=FALSE, install}
#library(devtools)
install_github("soodoku/domain_classifier/rdomains")
```

To install the package from CRAN, type in: 

```{r, eval=FALSE, cran_install}
install.packages("rdomains")
```

Next, load the package:

```{r, eval=FALSE, load_pkg}
library(rdomains)
```

#### Shalla

To get category of the content from [shallalist](http://www.shallalist.de), first download the latest file using:

```{r, eval=FALSE, down_shalla}
get_shalla_data()
```

And then, get the category using: 

```{r, eval=FALSE, shalla}
shalla_cat("http://www.google.com")
```

```
##   domain_name shalla_category
## 1  google.com   searchengines
```

#### DMOZ

To get category of the content from [DMOZ](dmoz.org), first download the archived parsed CSV file using:

```{r, eval=FALSE, down_dmoz}
get_dmoz_data()
```

And then, get the category using: 

```{r, eval=FALSE, dmoz}
dmoz_cat("http://www.google.com")
```

#### ML 

Probability that Domain Hosts Adult Content Based on features of Domain Name and Suffix alone: 

```{r, eval=FALSE, ml}
adult_ml1_cat("http://www.google.com")
```

```
##   domain_name  category
## 1  google.com 0.3133728
```

#### Virustotal

Start by getting the API key from [virustotal](https://www.virustotal.com/). 

Get virustotal category by running:

```{r, eval=FALSE, virustotal}
virustotal_cat("http://www.google.com")
```
```
##                 domain   bitdefender dr_web  alexa        google       websense             trendmicro
## 1 http://www.google.com searchengines  chats google searchengines advertisements search engines portals
```

#### Trusted (McAfee)

Get the content category of a domain according to McAfee (Trusted):

```{r, eval=FALSE, trusted}
trusted_cat("http://www.google.com")
```

```
##                    url          status   categorization   reputation
## 2 http://www.google.com Categorized URL - Search Engines Minimal Risk
```

#### Alexa Category

To get the category of content from Amazon (Alexa) (which provides it via DMOZ), start by getting credentials from [https://aws.amazon.com/](https://aws.amazon.com/). Next, set the environment variables:

```{r, eval=FALSE, set_alexa_cred}
Sys.setenv("AWS_ACCESS_KEY_ID", "key_id") 
Sys.getenv("AWS_SECRET_ACCESS_KEY", "secret_key")
```

Then run,

```{r, eval=FALSE, alexa}
alexa_cat(domain="http://www.google.com")[1,]
```

```
##                   Title                                           AbsolutePath
## 1 Search Engines/Google Top/Computers/Internet/Searching/Search_Engines/Google
```