---
title: "Using rdomains"
author: "Gaurav Sood"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Examples illustrating how to use rdomains}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

### rdomains: Get the category of content hosted by a domain

#### Install and Load the package

The latest version of the package will always be on GitHub. To install the package from GitHub and to load the installed package:

```{r, eval=FALSE, install}
devtools::install_github("soodoku/domain_classifier/rdomains")
library(rdomains)
```

#### Shalla

To get category of the content from shallalist:

```{r, eval=FALSE, shalla}
get_shalla_cat("http://www.google.com")
```

#### ML 

To get category of the content based on ML (currently gives propensity of pornographic content):

```{r, eval=FALSE, ml}
name_suffix_cat("http://www.google.com")
```

#### Virustotal

Start by getting the API key from [virustotal](https://www.virustotal.com/). 

Get virustotal category by running:

```{r, eval=FALSE, virustotal}

# virustotal_cat("http://www.google.com")
```

